Bericht Praxisphase I

### 2020-11-17 Paper.tex
page numbering
small fixes

		\small{%
			\begin{tabularx}{\textwidth}{@{}lX@{}}
				\toprule
				Bearbeitungszeitraum: & 24.10.2020 - 27.11.2020 \\
				Matrikelnummern, Kurs: & 7087727, 2686300, 1708267; TINF18-IT1 \\
				Vorlesung: & Verteilte Systeme \\
			\end{tabularx}
		}

@@

	\newpage
	\pagenumbering{Roman}

@@

		\vfill
		\noindent\rule{5cm}{.4pt}\hfill\rule{5cm}{.4pt}\par
		\noindent Datum, Ort \hfill Unterschrift

@@

	\pagenumbering{arabic}

	\chapter{Einführung}

@@

	\newpage

>>>>

		\small{%
			\begin{tabularx}{\textwidth}{@{}lX@{}}
				\toprule
				Bearbeitungszeitraum: & 24.10.2020 - 18.11.2020 \\
				Matrikelnummern, Kurs: & 7087727, 2686300, 1708267; TINF18-IT1 \\
				Vorlesung: & Verteilte Systeme \\
			\end{tabularx}
		}

@@

	\newpage
	\pagenumbering{gobble}

@@

		\vfill
		\quad 17.11.2020, Mannheim \\
		\noindent\rule{5cm}{.4pt}\hfill\rule{5cm}{.4pt}\par
		\noindent Datum, Ort \hfill Unterschriften

@@

	\chapter{Einführung}
		\pagenumbering{arabic}

@@

	\newpage
	\pagenumbering{gobble}
